### 2016-03-19 papers.tex
Add Stefan's SMACK review
papers.tex: Tweak page numbering height of page numbering paper

\addtrack{Half-track}{Crypticography}
\addpaper
	{Cryptographically secure page numbering in \LaTeX}
	{William Gunther and Brian Kell}
	{cryptography, hashing, LaTeX, macros, page numbers, security, SHA-256}
	{SIGBOVIK_2016_paper_18}
	{0cm}
	{\includegraphics[width=1in]{eval}}
\addreview{paper18eval}{-1.45cm}
\addpaper
	{Random seed generation}
	{Alexander R.\ Frieder}
	{random, seed, encryption, complexity, am, I, even, supposed, to, fill, this, out, what, amI, doing, ?}
	{SIGBOVIK_2016_paper_1}
	{0cm}
	{}

@@

\addtrack{Lamb track}{Languages: Human and... Inhuman}
\addpaper
	{Lambda Doge: A digital canine language}
	{Joshua Suereth}
	{lambda calculus, doge, programming languages}
	{SIGBOVIK_2016_paper_15}
	{0cm}
	{}
\addpaper
	{Making the theoretical possible: the untyped $\lambda$-calculus in C++}
	{Jim McCann}
	{lambda, c++, c++11}
	{SIGBOVIK_2016_paper_23}
	{0cm}
	{}
\addpaper
	{ShAIkespeare in the modern age}
	{Abida Haque}
	{Shakespeare, AI, semantic networks, frames, intelligence}
	{SIGBOVIK_2016_paper_25}
	{0cm}
	{}
\addpaper
	{A shortmantout}
	{David Renshaw and Jim McCann}
	{portmanteausteritycoon, hotshots, carthartichokes, sadjustment}
	{SIGBOVIK_2016_paper_13}
	{0cm}
	{}

@@

\addtrack{Cattle track}{Higher-order Research}
\addpaper
	{On the topic of "um..."}
	{Timothy J.\ Parenti}
	{um, best, paper}
	{SIGBOVIK_2016_paper_20}
	{-0.55cm}
	{}
\addreview{review-bestpaper}{0cm}
\addpaper
	{SMACK: When research in algorithms goes around in circles}
	{Patrick Lin and Weishuang Linda Xu}
	{algorithms, collider, particle physics}
	{SIGBOVIK_2016_paper_4}
	{-2cm}
	{}
\addpaper
	{A look into the mind of the modern graduate student via telephonic obfuscation}
	{Erik Harpstead \textit{et al.}}
	{comestibility theory, telephonic obfuscation, computer human interaction}
	{SIGBOVIK_2016_paper_6}
	{0cm}
	{}
\addpaper
	{Dinner grant renewal request}
	{From Dr.\ Angus McNabb III to Jim McCann}
	{dinner, dog pictures, naps, napping, nap time, sleeping}
	{SIGBOVIK_2016_paper_14}
	{0cm}
	{}
\addpaper
	{Ode to reviewer two}
	{Anonymous}
	{ode, double-blind review, false politeness, landslide}
	{SIGBOVIK_2016_paper_7}
	{0cm}
	{}

>>>>

\addtrack{Half-track}{Crypticography}
\addpaper
	{Cryptographically secure page numbering in \LaTeX}
	{William Gunther and Brian Kell}
	{cryptography, hashing, LaTeX, macros, page numbers, security, SHA-256}
	{SIGBOVIK_2016_paper_18}
	{-2cm}
	{\includegraphics[width=1in]{eval}}
\addreview{paper18eval}{-1.45cm}
\addpaper
	{Random seed generation}
	{Alexander R.\ Frieder}
	{random, seed, encryption, complexity, am, I, even, supposed, to, fill, this, out, what, amI, doing, ?}
	{SIGBOVIK_2016_paper_1}
	{0cm}
	{}

@@

\addtrack{Lamb track}{Languages: Human and... Inhuman}
\addpaper
	{Lambda Doge: A digital canine language}
	{Joshua Suereth}
	{lambda calculus, doge, programming languages}
	{SIGBOVIK_2016_paper_15}
	{0cm}
	{}
\addpaper
	{Making the theoretical possible: the untyped $\lambda$-calculus in C++}
	{Jim McCann}
	{lambda, c++, c++11}
	{SIGBOVIK_2016_paper_23}
	{0cm}
	{}
\addpaper
	{ShAIkespeare in the modern age}
	{Abida Haque}
	{Shakespeare, AI, semantic networks, frames, intelligence}
	{SIGBOVIK_2016_paper_25}
	{0cm}
	{}
\addpaper
	{A shortmantout}
	{David Renshaw and Jim McCann}
	{portmanteausteritycoon, hotshots, cathartichokes, sadjustment}
	{SIGBOVIK_2016_paper_13}
	{0cm}
	{}

@@

\addtrack{Cattle track}{Higher-order Research}
\addpaper
	{On the topic of "um..."}
	{Timothy J.\ Parenti}
	{um, best, paper}
	{SIGBOVIK_2016_paper_20}
	{-0.55cm}
	{}
\addreview{review-bestpaper}{0cm}
\addpaper
	{SMACK: When research in algorithms goes around in circles}
	{Patrick Lin and Weishuang Linda Xu}
	{algorithms, collider, particle physics}
	{SIGBOVIK_2016_paper_4}
	{-2cm}
	{}
\addreview{review-smack}{0cm}
\addpaper
	{A look into the mind of the modern graduate student via telephonic obfuscation}
	{Erik Harpstead \textit{et al.}}
	{comestibility theory, telephonic obfuscation, computer human interaction}
	{SIGBOVIK_2016_paper_6}
	{0cm}
	{}
\addpaper
	{Dinner grant renewal request}
	{From Dr.\ Angus McNabb III to Jim McCann}
	{dinner, dog pictures, naps, napping, nap time, sleeping}
	{SIGBOVIK_2016_paper_14}
	{0cm}
	{}
\addpaper
	{Ode to reviewer two}
	{Anonymous}
	{ode, double-blind review, false politeness, landslide}
	{SIGBOVIK_2016_paper_7}
	{0cm}
	{}
